### 2021-07-05 README.Rmd

<!-- badges: start -->
[![rOpenSci Badge](https://badges.ropensci.org/87_status.svg)](https://github.com/ropensci/onboarding/issues/87)[![JOSS status](http://joss.theoj.org/papers/c85f57adbc565b064fb4bfc9b59a1b2a/status.svg)](http://joss.theoj.org/papers/c85f57adbc565b064fb4bfc9b59a1b2a)[![DOI](https://zenodo.org/badge/50553382.svg)](https://zenodo.org/badge/latestdoi/50553382)[![R-CMD-check](https://github.com/ropensci/visdat/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/visdat/actions)[![Codecov test coverage](https://codecov.io/gh/ropensci/visdat/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/visdat?branch=master)[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/visdat)](https://cran.r-project.org/package=visdat)[![CRAN Logs](http://cranlogs.r-pkg.org/badges/visdat)](http://cran.rstudio.com/web/packages/visdat/index.html)[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
<!-- badges: end -->

@@

- `vis_miss()` visualises just the missing data, and allows for missingness to
be clustered and columns rearranged. `vis_miss()` is similar to
`missing.pattern.plot` from the
[`mi`](https://cran.r-project.org/web/packages/mi/index.html) package.
Unfortunately `missing.pattern.plot` is no longer in the `mi` package (as of
14/02/2016).

@@

Please note that the visdat project is released with a [Contributor Code of Conduct](http://visdat.njtierney.com/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

@@

Thank you to Ivan Hanigan who [first
commented](http://www.njtierney.com/r/missing%20data/rbloggers/2015/12/01/ggplot-missing-data/#comment-2388263747)
this suggestion after I made a blog post about an initial prototype
`ggplot_missing`, and Jenny Bryan, whose
[tweet](https://twitter.com/JennyBryan/status/679011378414268416) got me
thinking about `vis_dat`, and for her code contributions that removed a lot of
errors.

@@

Finally thank you to [rOpenSci](https://github.com/ropensci) and it's amazing
[onboarding process](https://github.com/ropensci/onboarding), this process has
made visdat a much better package, thanks to the editor Noam Ross (@noamross),
and the reviewers Sean Hughes (@seaaan) and Mara Averick (@batpigandme).

>>>>

<!-- badges: start -->
[![rOpenSci Badge](https://badges.ropensci.org/87_status.svg)](https://github.com/ropensci/software-review/issues/87)[![JOSS status](https://joss.theoj.org/papers/10.21105/joss.00355/status.svg)](https://joss.theoj.org/papers/10.21105/joss.00355)[![DOI](https://zenodo.org/badge/50553382.svg)](https://zenodo.org/badge/latestdoi/50553382)[![R-CMD-check](https://github.com/ropensci/visdat/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/visdat/actions)[![Codecov test coverage](https://codecov.io/gh/ropensci/visdat/branch/master/graph/badge.svg)](https://codecov.io/gh/ropensci/visdat?branch=master)[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/visdat)](https://cran.r-project.org/package=visdat)[![CRAN Logs](http://cranlogs.r-pkg.org/badges/visdat)](https://CRAN.R-project.org/package=visdat)[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/)
<!-- badges: end -->

@@

- `vis_miss()` visualises just the missing data, and allows for missingness to
be clustered and columns rearranged. `vis_miss()` is similar to
`missing.pattern.plot` from the
[`mi`](https://CRAN.R-project.org/package=mi) package.
Unfortunately `missing.pattern.plot` is no longer in the `mi` package (as of
14/02/2016).

@@

Please note that the visdat project is released with a [Contributor Code of Conduct](https://github.com/ropensci/visdat/blob/master/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.

@@

Thank you to Ivan Hanigan who [first
commented](https://www.njtierney.com/post/2015/11/12/ggplot-missing-data/)
this suggestion after I made a blog post about an initial prototype
`ggplot_missing`, and Jenny Bryan, whose
[tweet](https://twitter.com/JennyBryan/status/679011378414268416) got me
thinking about `vis_dat`, and for her code contributions that removed a lot of
errors.

@@

Finally thank you to [rOpenSci](https://github.com/ropensci) and it's amazing
[onboarding process](https://github.com/ropensci/software-review), this process has
made visdat a much better package, thanks to the editor Noam Ross (@noamross),
and the reviewers Sean Hughes (@seaaan) and Mara Averick (@batpigandme).
